Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-05-29 paper.tex
Doing things in no particular order

		\noindent The typicality of a concept is a topic that needs a lot of exploration, since it's difficult to evaluate precisely the typicality of an object 
		and also because the people's brains are always a little different from each other. The experiment I would like to propose, has the objective of 
		making us understand better the bond between the perceived typicality of an object that belongs to a category and the prototype of that category.
		This can help the scientists to better understand how knowledge is organized in the brain. This experiment consists in different phases, such as
		data collection, feature extraction, prototype construction and similarity judgment.

@@

@@

				\begin{figure}[!ht]
					\centerline{\includegraphics[width=\linewidth]{imgs/obama_histogram.png}}
					\caption{Example of color histogram}
					\label{fig:2}
				\end{figure}

@@

					\noindent In 2019, Guamei et al. wrote a paper about hybrid feature extraction methods to classify brain tumours~\cite{gumaei2019hybrid}. The process described in the paper is divided into three points. The 
					first one is preprocessing, the second is feature extraction and the third is brain tumour classification. The first step is just to rescale the values to the range $[0,\ 1]$. The feature extractor 
					used is the GIST descriptor. The GIST is then combined with a Gabor filter and produces a total of $mxnx4x4$ GIST feature vectors. There is a variant of the GIST descriptor, the 
					PCA-NGIST is a PCA-based normalized GIST feature extraction method. The NGIST is a normalized version of the GIST descriptor, that uses the L2 norm to make the GIST invariant to illumination and shadowing. 
					After this step, the only thing left is the classification of the tumour, which was performed with a RELM classifier.

@@

			\noindent Since the proposed experiment uses neural networks, there is the need to have a lot of data. In this particular case, there is the need to gather many images. There are some image dataset, intended for computer 
			vision~\footnote{\url{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}}, that could help. Some of the dataset reported there are famous, like ImageNet or Google's Open Images. The 
			best for this kind of work, though, is to have a dataset that bases every image on the same ``macro-category'', like for example a dataset made of images of birds.

		\subsection{Typicality values}

			\noindent In this experiment, typicality judgments play a crucial role. To gather enough data about the perceived typicality of images, a form is necessary. This survey should be structured in a way that presents an 
			image ad a time to the subject that is taking the survey and asks to rate the typicality of the object portrayed in the image, possibly in a given range. If that's the case, a range between $1$ and $10$ 
			could be the best decision since people are quite used to rate in this range. Once there are enough results, the various rates should be averaged so that there is a single measure that takes into 
			account every rate taken from the survey. The number of people that should participate in the experiment should be high enough to be a meaningful statistical group.

@@

		\noindent While collecting the needed data with the survey, it's possible to begin the feature extraction procedure. There are various possibilities for this step, as shown in the Section dedicated to feature extraction background. 
		It could be interesting to test both classical and machine learning methods, to measure which one is the most efficient. Since feature extraction has already been described in the paper, this section will 
		present a discussion about the results of the presented methods' results. The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
		In fact, for classical feature extraction techniques, humans have no difficulty in interpreting the result of the process. For example, in edge extraction, humans have no difficulty in recognizing if the 
		edge extracted is correct or not seeing the original image. For example, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left, 
		while in Figure \ref{fig:4} there is no clear correlation between the feature and what it means in the image itself.
		Moreover, classical and machine learning features can give different weights to different features. 
		In fact, classical methods rely on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works. An empirical confirmation of this fact 
		can be that if a person asks to another person to describe, for example, a common kingfisher, the person that should describe the bird will, most likely, start describing the dimension, the shape, and only 
		later the colour. Machine learning techniques, on the other hand, could give a very high importance to the fact that the bird is mainly blue and red, if they have access to the colour information. Due to the fact that 
		the blue colour is not very present in nature, the blue and red couple of colours can be highly characteristic of the common kingfisher, even if humans give, unconsciously and innately, more importance to 
		shape-related features.

@@

			\noindent In case machine learning feature extraction techniques were used, it's conceptually and practically easier to compute the average features. In fact, the features extracted by machine learning techniques are 
			in the form of arrays of numbers, so to compute the prototype of the image in this form it's enough to take the weighted average of the vectors.

		\subsection{Considerations about prototype construction}

			\noindent The prototype depends on the feature extraction technique that was used. As discussed in Section \ref{sec:fe}, the key difference is human interpretability. In fact, building a prototype using the 
			classical feature extraction methods, results in an image that can be seen and interpreted. Using a prototype generated with machine learning feature extraction techniques results in an array 
			of numerical values, that are not easily interpretable. As of 2022, there has been some research on the topic of interpretability and explainability of machine learning, like for example 
			a work by Carvalho written in 2019, %(\textbf{SOME CITATIONS}),
			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the european union in the field of artificial intelligence. In particular, there is a document of 
			the act~\footnote{\url{https://eur-lex.europa.eu/resource.html?uri=cellar:e0649735-a372-11eb-9585-01aa75ed71a1.0001.02/DOC_1&format=PDF}} that states that there will be some requirements in terms of 
			transparency and intepretability for machine learning systems that are considered high-risk AI. The growing interest produced some results, but still they're not enough to easily interpret machine learning 
			features.\\
			Most likely, in the future will be possible to look at the features extracted by a neural network and comprehend their meaning. When this will be possible, independently of the feature extraction techniques 
			used, the human interpretability will be possible, and with that in mind it would be probably more convenient to extract the features using neural networks. The reason behind this consideration is 
			that although the training of a neural network can be expensive in computational terms, the evaluation of an input on a trained network it's not very computationally demanding. On the other side, algorithms 
			like the triangulation always have the same demand, that is lower than the demand of training a neural network, but surely higher than the demand of evaluating a single input on a neural network. 
			Moreover, considering the possiblity to use transfer learning techniques, the training can become a fine-tuning or a domain adaptation, which means the computational load is lighter. Considering that 
			the fact that the training is a demanding task to be perfomed only once and that other algorithms may be less demanding but must be run multiple times, it's probably more convenient to train a neural 
			network. Moreover, not only the feature extraction process is convenient, but also the prototype construction itself is more convenient if the features are in the form of numerical parameters, since it's 
			enough to perform a weighted average, a simpler operation if confronted with the construction of a new image that should take into account features of numerous other images.

@@

		\noindent The similarity learning is the core part of the experiment. In this experiment, the similarity learning is done through a siamese neural network but, as the previous steps, its architecture depends on the 
		feature extraction techniques used.

@@

			\noindent If the feature extraction process happened with classical techniques, after the prototype building step the result is an image. This means that the two embedding networks must be able to process 
			images. Most likely, the best choice, in this case, is to implement two CNNs as embedding networks and merge them in a single fully connected network for the siamese similarity learning. 
			In this case, the siamese network would be fed the prototype image and the an image from the dataset. The goal of this kind of prediction is to learn a similarity metric with some annotated values. 
			After learning the similarity metric, the network will be able to measure the similarity of the prototype image and any other image fed in the other embedding network. By doing so and retrieving various 
			measurements the couple of values \textit{perceived typicality - similarity measure} could reveal some interesting patterns.

			\noindent If the feature extraction process involved neural networks, after the prototype building step the result is not anymore an image but it's a vector of values. This implies that there is no need to 
			use a convolutional neural network as embedding, but it's enough to have some fully connected layers that will be merged in a single fully connected network for the similarity learning. The rest of the procedure 
			is similar, since the siamese network will still be fed the features of the prototype and the features of an imaage of the dataset.

@@

			\noindent The loss function is a key factor of this kind of leaning, togheter with the distance measure. In fact, siamese neural networks usually use a loss function that is called contrastive loss. This kind 
			of loss is based on a distance measure that should be defined by the person doing the experiment. The type of measure that it's possible to use ranges a lot, from simple distances like the manhattan distance 
			or the euclidean distance to more complex measures that can be defined by the user.

		% Word count without this section: 4526
		\subsection{Considerations about similarity learning}

			% 
			\noindent

	\section{Possible Further Experiments\label{sec:pfe}}

@@

		\subsection{Possible relevant follow-ups of similarity learning}

@@

>>>>

		\noindent The typicality of a concept is a topic that needs a lot of exploration, since it's difficult to evaluate precisely the typicality of an object 
		and also because the people's brains are always a little different from each other. The experiment I would like to propose, has the objective of 
		making us understand better the bond between the perceived typicality of an object that belongs to a category and the prototype of that category.
		This experiment consists in different phases, such as data collection, feature extraction, prototype construction and similarity judgment.

	\section{Applications}

		\noindent The possible applications of this experiment are widely ranged. First of all, this experiment could help neuroscientists understand how the knowledge is 
		organized in the brain. By doing so, there is the possibility to increase the knowledge about the brain and how it works. Moreover, it's possible to confront 
		the way that a person with cognitive disorders or, more generally, some kind of mental disorder related to knowledge with the results of people without 
		any disorder, trying to understand if the way that knowledge is handled in the brain is somehow similar or completely different. Lastly, this experiment can 
		also help to understand if knowledge is encoded in a similar way in artificial and biological neural systems.

@@

		\subsection{Typicality}

			\noindent Typicality is one of the key concepts that will be used in this paper, so it's fundamental that it's defined. In a paper by Dieciuc and Folstein~\cite{dieciuc2019typicality},
			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
			despite their difference, minimizing the differences and maximizing the similarities. So typicality is, in this paper, defined  a measure of how representative an example is of their category and 
			of the other members of the same category.

@@

				\begin{figure}[!ht]
					\centerline{\includegraphics[width=\linewidth]{imgs/obama_histogram.png}}
					\caption{Color histogram of the image used in \ref{fig:1}}
					\label{fig:2}
				\end{figure}

@@

					\noindent In 2019, Guamei et al. wrote a paper about hybrid feature extraction methods to classify brain tumours~\cite{gumaei2019hybrid}. The process described in the paper is divided into three points. The 
					first one is preprocessing, the second is feature extraction and the third is brain tumour classification. The first step is just to rescale the values to the range $[0,1]$. The feature extractor 
					used is the GIST descriptor. The GIST is then combined with a Gabor filter and produces a total of $mxnx4x4$ GIST feature vectors. There is a variant of the GIST descriptor, the 
					PCA-NGIST is a PCA-based normalized GIST feature extraction method. The NGIST is a normalized version of the GIST descriptor, that uses the L2 norm to make the GIST invariant to illumination and shadowing. 
					After this step, the only thing left is the classification of the tumour, which was performed with a RELM classifier.

@@

			\noindent Since the proposed experiment uses neural networks, there is the need to have a lot of data. In this particular case, there is the need to gather many images. There are some image dataset, intended for computer 
			vision~\footnote{\url{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}}, that could help. Some of the dataset reported there are quite famous, like ImageNet or Google's Open Images. The 
			best for this kind of work, though, is to have a dataset that bases every image on the same ``macro-category'', like for example a dataset made of images of birds. Even though this is the ideal case,
			most of the dataset that are used for computer vision contain more than one single category. For example, ImageNet, which is one of the most famous image datasets, contains more than 1 million images that are divided 
			into 1000 classes. Generally, it's possible to use these datasets, which have different macro categories by filtering the input images based on the macro category the experiment is based on.

		\subsection{Typicality values\label{sec:typval}}

			\noindent In this experiment, typicality judgments play a crucial role. To gather enough data about the perceived typicality of images, a form is necessary. This survey should be structured in a way that presents an 
			image at a time to the subject that is taking the survey and asks to rate the typicality of the object portrayed in the image, possibly in a given range. If that's the case, a range between $1$ and $10$ 
			could be the best decision since people are quite used to rate in this range. Once there are enough results, the various rates should be averaged so that there is a single measure that takes into 
			account every rate taken from the survey. The number of people that should participate in the experiment should be high enough to be a meaningful statistical group.

		\subsection{Possible alternative to typicality values\label{sec:patv}}

			Another possibility to gather data, it's to ask people to list a certain number of objects or all the objects they can think about of the decided category. For example, let's assume the macro category decided 
			is ``birds''. It's possible to collect enough data by asking people to list a the first few examples of birds, using a predefined number. Moreover, it's possible to use a variant of this procedure and ask people 
			to list all the examples of birds that they can think of. These two variants of the same data collection approach are both possible and come with some advantages and disadvantages when compared to the other 
			method described in \ref{sec:typval}. % In case this type of data collection is used, the values of typicality should be also a question that asks the subjects to describe all the features that birds have in common 
			% with each other. This step will then be used for prototype construction.

		\subsection{Considerations about the survey}

			The two presented methods proposed for data collection are very different. Both of these have their own pros and cons. The first method can help in having a typicality value for every image collected in the dataset, 
			while the second does not. The large number of images that should be used, though, it's not feasible to ask the subjects to rate the typicality value of all the images of the dataset. In fact, it's very likely 
			that a subject that has to rate the typicality of a large number of images will be tired after a certain number of images, polluting the results of the survey. A possible solution to this problem is to 
			divide the survey so that subjects have to rate the typicality of a limited number of images. This method would result in a lower amount of data, but at the same time, a more precise amount of data. Another 
			problem with this method it's that it has a possible bias. In fact, if a person sees a bird, for example a swan, or a duck, and is asked to rate its typicality, most likely will rate it in the higher part 
			of the scale, while if asked to list a certain number of birds it's more likely that it's not present than that it's present.\\
			On the other hand, the second method gives a possibly lower bias, since there are no images that can influence the subject's mind showing images of examples of the category that the subject didn't think of. 
			Recalling the previous example with the swan, if a person does not think of the swan, it won't be present in the list created by the subject. This could result in a lower bias, but it comes at the cost 
			of having to interview more people and, most likely, not having enough data for some of the examples. In this approach, the more a bird is typical, the more it appears in the lists and in higher positions. 
			There is an example in the appendix. Even though this method has the advantage of having less bias, has a  great drawback. That is, in particular, the fact that the prototype construction is very difficult.\\
			In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two 
			methods and decide which one is more convenient.
			As alternative, it's possible to try both the methods and see which one gives better results. In this way, both the possibilities will be used and there is the possibility to see which one is better in 
			terms of performance.

@@

		\noindent While collecting the needed data with the survey, it's possible to begin the feature extraction procedure. There are various possibilities for this step, as shown in the Section dedicated to feature extraction background. 
		It could be interesting to test both classical and machine learning methods, to measure which one is the most efficient. Since feature extraction has already been described in the paper, this section will 
		present a discussion about the results of the presented methods' results. The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
		In fact, for classical feature extraction techniques, humans have no difficulty in interpreting the result of the process. For example, in edge extraction, humans have no difficulty in recognizing if the 
		edge extracted is correct or not seeing the original image. For example, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left, 
		while in Figure \ref{fig:4} there is no clear correlation between the feature and what it means in the image itself.
		Moreover, classical and machine learning features can give different weights to different features. 
		In fact, classical methods rely mostly on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works. An empirical confirmation of this fact 
		can be that if a person asks to another person to describe, for example, a common kingfisher, the person that should describe the bird will, most likely, start describing the dimension, the shape, and only 
		later the colour. Machine learning techniques, on the other hand, could give a very high importance to the fact that the bird is mainly blue and red, if they have access to the colour information. Due to the fact that 
		the blue colour is not very present in nature, the blue and red couple of colours can be highly characteristic of the common kingfisher, even if humans give, unconsciously and innately, more importance to 
		shape-related features.	\\
		If the data collection method chosen is the one that asks people to list the objects of the category, the feature extraction can happen in two possible ways. The first way is to use the data collected for 
		typicality judgments and collect also images of the birds that appear in the results. After collecting enough images, the feature extraction process can proceed as described earlier and use either  
		classical or machine-learning-based feature extraction methods. Although this is a possibility, there could be an alternative. The alternative seems interesting because it can be adapted to rely only on features 
		that humans identify as important. To do so, the survey should include a question that asks the subjects to list all the characteristics that the objects of the given macro category have in common. In this case, 
		the features are not strictly extracted by the dataset, but are listed by the subjects that take part in the survey. By doing so, the experiment takes into account, in the prototype, only the features that 
		human have listed, so only the features that are considered important by humans themselves. Although it's theoretically possible, this procedure will result in numerous complication in prototype construction.

@@

			\noindent In case machine learning feature extraction techniques were used, it's conceptually and practically easier to compute the average features. In fact, the features extracted by machine learning techniques are 
			in the form of arrays of numbers, so to compute the prototype of the image in this form it's enough to take the weighted average of the vectors. 
			%Allungare (?)

		\subsection{Other survey method}

			%Diificile, da pensare bene.

		\subsection{Considerations about prototype construction\label{sec:cpc}}

			\noindent The prototype depends on the feature extraction technique that was used. As discussed in Section \ref{sec:fe}, the key difference is human interpretability. In fact, building a prototype using the 
			classical feature extraction methods, results in an image that can be seen and interpreted. Using a prototype generated with machine learning feature extraction techniques results in an array 
			of numerical values, that are not easily interpretable. As of 2022, there has been some research on the topic of interpretability and explainability of machine learning, like for example 
			a work by Carvalho written in 2019~\cite{electronics8080832}, %(\textbf{SOME CITATIONS}),
			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the european union in the field of artificial intelligence. In particular, there is a document of 
			the act~\footnote{\url{https://eur-lex.europa.eu/resource.html?uri=cellar:e0649735-a372-11eb-9585-01aa75ed71a1.0001.02/DOC_1&format=PDF}} that states that there will be some requirements in terms of 
			transparency and intepretability for machine learning systems that are considered high-risk AI. The growing interest produced some results, but still they're not enough to easily interpret machine learning 
			features.\\
			Most likely, in the future will be possible to look at the features extracted by a neural network and comprehend their meaning. When this will be possible, independently of the feature extraction techniques 
			used, the human interpretability will be possible, and with that in mind it would be probably more convenient to extract the features using neural networks. The reason behind this consideration is 
			that although the training of a neural network can be expensive in computational terms, the evaluation of an input on a trained network it's not very computationally demanding. On the other side, algorithms 
			like the triangulation always have the same demand, that is lower than the demand of training a neural network, but surely higher than the demand of evaluating a single input on a neural network. 
			Moreover, considering the possiblity to use transfer learning techniques, the training can become a fine-tuning or a domain adaptation, which means the computational load is lighter. Considering that 
			the fact that the training is a demanding task to be perfomed only once and that other algorithms may be less demanding but must be run multiple times, it's probably more convenient to train a neural 
			network. Moreover, not only the feature extraction process is convenient, but also the prototype construction itself is more convenient if the features are in the form of numerical parameters, since it's 
			enough to perform a weighted average, a simpler operation if confronted with the construction of a new image that should take into account features of numerous other images.

@@

		\noindent The similarity learning is the core part of the experiment. In this experiment, the similarity learning is done through a siamese neural network but, as the previous steps, depends on the 
		feature extraction techniques used.

@@

			\noindent If the feature extraction process happened with classical techniques, after the prototype building step the result is an image. This means that the two embedding networks must be able to process 
			images. Most likely the best choice, in this case, is to implement two CNNs as embedding networks and merge them in a single fully connected network for the siamese similarity learning. 
			In this case, the siamese network would be fed the prototype image and an image from the dataset. The goal of this kind of prediction is to learn a similarity metric with some annotated values. 
			After learning the similarity metric, the network will be able to measure the similarity of the prototype image and any other image fed in the other embedding network. By doing so and retrieving various 
			measurements the couple of values \textit{perceived typicality - similarity measure} could reveal some interesting patterns.

			\noindent If the feature extraction process involved neural networks, after the prototype building step the result is not anymore an image but it's a vector of values. This implies that there is no need to 
			use a convolutional neural network as embedding, but it's enough to have some fully connected layers that will be merged in a single fully connected network for the similarity learning. The rest of the procedure 
			is similar, since the siamese network will still be fed the features of the prototype and the features of an imaage of the dataset. As in the previous case, the goal of this kind of prediction is to learn 
			a similarity metric using annotated values. After learning the metric, the network will be able to measure the similarity of the prototype and any other image. 
			By doing so the couple of values \textit{perceived typicality - similarity measure} could reveal some interesting patterns.

@@

			\noindent The loss function is a key factor of this kind of leaning, together with the distance measure. In fact, siamese neural networks usually use a loss function that is called contrastive loss. This kind 
			of loss is based on a distance measure that should be defined by who is conducting the experiment. The type of measure that it's possible to use ranges a lot, from simple distances like the Manhattan distance 
			or the euclidean distance to more complex measures that can be defined by the user.

		\subsection{Considerations about similarity learning\label{sec:csl}}

			\noindent The two possible embedding networks, convolutional and fully connected, lead to different internal results but the final goal is the same. In fact, even if with different computations, the siamese 
			network outputs a similarity measure. This output strongly relies on the distance measure. In fact, the same two vectors can have different similarity measures, based on the type of distance that the user 
			decided to implement. For example, suppose that the vectors are $[2,\ 3]$ and $[5, 8]$. If the Manhattan distance is chosen as measure, the distance between the two defined vectors is $8$. 
			Using the euclidean distance instead of the Manhattan distance, the result is $~5,83$. In data science there are some possibilities for distance measurements, a part from euclidean and Manhattan distance. Some 
			examples are the cosine distance or the Hamming distance. Moreover, there could be an ad hoc distance measure, defined for this problem in order to optimize the results obtained by the neural network. 
			This kind of freedom is very beneficial, since it gives the possibility to use different formulas and, seeing the results, there is also the possibility to see which distance works better. This could give an 
			insight on which one of the distance measures is the closest to the one used by human brain in similarity judgement. \\
			Focusing more on the computational aspect of the similarity learning, the more convenient approach is the one involving neural networks feature extraction. In fact, if the features are extracted with 
			neural networks, the siamese network will only need fully connected layers, while it would need convolutional, pooling and fully connected layers if the features are extracted with in a classical way. 
			The only problem about the machine learning feature extraction techniques is, as mentioned in \ref{sec:cpc}, is the fact that we're still unable to interpret the features extracted by a CNN.

	\section{Possible Further Experiments}

@@

			\noindent The siamese network described in \ref{sec:csl} has no constraints about both the distance measure and the loss function. An interesting possibility could be using a distance measure that is sensitive 
			to human similarity judgments. In this way, the network will optimize the weights in order to predict based on the human similarity measure. The resulting similarity measure can be, in this case, 
			compared with the state-of-art human similarity judgments obtained with CNNs.\\
			Another possibility is to adopt a variant of the previously described network. For example, it's possible to use a variant of siamese neural networks that uses triplets for training. In this version, 
			the network takes in input a reference (which is the prototype in the case of this experiment) and two values, one positive and one negative. The network tries to maximize the distance between the reference and 
			the negative example, while minimizing the distance between the reference and the positive example. There is a way, as shown by Dor et al. in \cite{ein-dor-etal-2018-learning}, to adapt the triplet 
			network to learn a similarity metric. In this way, the similarity metric is learned and so the network itself tries to optimize it. There are different research papers that show how triplet networks 
			usually outperform siamese networks, especially in one-shot learning. Could be interesting, in this experiment, to confront both siamese neural networks and triplet networks to see which performs better. 
			Moreover, this could give some hints on how the human similarity judgments work.

		\subsection{Possible relevant experiments}

			\noindent One of the first ideas that is an interesting follow-up of this experiment is to compare the results obtained with the two possible feature extraction methods. Even though one of the two methods is not 
			interpretable by humans, it's still interesting trying to understand which of the methods is more efficient in detecting features relevant for the similarity learning. Moreover, if the results 
			indicate that the machine learning techniques are more efficient, could be a push in the research that try to understand the neural networks' feature extraction method. This could be interesting 
			for the future of neural networks and neuroscience. \\
			After the described experiment, there are some natural extensions of the experiment. One of the most natural and obvious extensions of the experiment is to try the same experiment with another category 
			of images. For example, if the first experiment is conducted on a dataset with bird images, it could be interesting to conduct the same experiment on a dataset that uses a different animal, like, for 
			example, fishes.\\
			Another experiment that comes as natural is trying to apply some transfer learning techniques. This could be interesting because, as far as we know, the human brain similarity can work 
			in different ways in judging similarity of different images. Applying transfer learning, we could see if the feature extracted for a category are also effective for a different category. This can give 
			extra insight about the typicality and its perception and how it works in human brain. The results can show that human brain innately use the same kind of measure of typicality or a different measure of 
			typicality for different classes. Of course, either result should be investigated more, since a single test is not enough to prove that one of the two possibilities is more likely than the other. Even though 
			it's not enough for a proof, could be an interesting starting point for neuroscientists to better understand how typicality works in human brain.\\
			Another possibly interesting topic could be examining the results of the survey based on the region of the person answering. In fact, it's possible that different regions, that have slightly different 
			cultures and that may result in slightly different typicality perception. For example, in Europe the eagles are not common, so it's very likely that people will give a high typicality to eagles, while 
			in North America, since the bald eagle is a national symbol, it's easier that people associate with it a higher typicality value. Moreover, there are a lot of different factors that can influence 
			the typicality rates of images in people. For example, a farmer could be more inclined than people that live in a big city to think associate a chicken with the concept of ``bird'', and thus giving 
			it a higher typicality.\\
			Lastly, it's worth notice that in this paper the prototype is considered as the mean of the features extracted from all the the images of the dataset. A possibility that could be interesting would be 
			interesting to try to experiment the possibility to use different concept of prototype and implementing the correspondent methods of building it.\\
			% Cognitive/learning disorders (?)

@@

		The experiment proposed has the objective to help identifying, if it exists, a link between the typicality of a concept and the similarity to a prototype. The work strongly relies on neural networks, in 
		particular siamese networks, and using them tries to achieve the goal of linking similarity of a prototype with the typicality. Both if the siamese network can achieve good statistics or if it cannot achieve 
		good statistics, the result can give an idea of the correlation between typicality and a prototype of a concept.

	\appendix

	\section{Appendix\label{sec:app}}

		To test the method of data collection described in \ref{sec:patv}, I collected the results of a small survey in which there were 10 questions, each asking to give the name of a bird. The number of 
		people that answered is not big enough to be a statistically relevant group, since the number of the answers is only $14$.

		\begin{figure*}
			\centerline{\includegraphics[width=\linewidth]{imgs/survey_hist.png}}
			\caption{Results of the survey}
			\label{fig:app}
		\end{figure*}

		\noindent In Figure \ref{fig:app} there are the results of the survey. Even though the number of answers was not very big, some problems were still emerged.
		\begin{itemize}

			\item \textbf{Off-topic answers or blank answers}:

				\noindent In this case, one of the answers had to be deleted from the answers, since the cited example was not part of the category decided for the survey. In particular, the survey asked for examples of birds, 
				while one of the answers was ``gazelle''. This fact highlights a problem bound to the number of examples the user knows or can think of. In this example, the survey asked for $10$ names of birds,
				which I thought was a reasonable number, but probably some of the subjects that took part to this survey could not think of a $10^{th}$ name, so just put a name of another animal. The solution 
				to this problem is to apply some data cleaning to the answers to filter the examples that, eventually, are in the answers but not part of the given category. An analogue approach can be applied if the 
				subject leaves the answer blank for the same reason.

			\item \textbf{Capitalization of examples}:

				\noindent This problem is simpler than the previous one to solve, since it just involves the capitalization of the answers. If the survey starts accounting numerous results, it becomes difficult to 
				compute the number of times that a particular example appears in the answers, so, most likely, there will be some automated scripts that compute all the needed statistics. This could be a problem since 
				in most of the programming languages, if not all, words like ``Robin'' and ``robin'' are considered different based on the capitalization. This problem is easily solvable by lowercasing all the 
				answers.

			\item \textbf{Typos of examples}:

				\noindent This problem can be quite challenging to solve. In fact, subjects could make some mistakes when typing the answers, so for example a word like ``robin'' can become ``ribin'' or ``tobin'' for example. 
				Moreover, if more than one letter is wrong, some results like ``rivim'' instead of ``robin'' are possible, especially if the subjects compile the form via mobile devices. To solve this issue, 
				it's possible to use some distance between strings, like for example the Levenshtein distance, which is frequently used to find the distance between two strings. Although this could be a solution,
				it's not guaranteed that the result is correct, so these results should always be checked again to prove they are correct and, most importantly, coherent with the category the survey is based on.

			\item \textbf{Different specificity levels}:

				\noindent This problem is very difficult to overcome. There is an example in the histogram reported as results. In the histogram, in fact, it's possible to note that there are both the ``eagle'' and 
				the ``bald eagle'' labels. This means that different subjects can answer with different levels of specificity, since the ``eagle'' label is more general than its counterpart ``bald eagle''. 
				This problem is presented also in an inter-species context, for example the ``Common kingfisher'' represents a single specie, representative of the ``kingfisher'' genus, while, for example, 
				``Flamingo'' represents a family, of which some examples are the greater flamingo and the lesser flamingo, along with other species as well. 
				Even though the problem is very clear, it's not very clear what to do in this case. A possibility is to decide that, in this case, the ``bald eagle'' label should be incorporated in the ``eagle'' 
				label, making sure that all the instances of the most specific one are accounted as instances of the more general one. Another possibility is to keep both of the labels, so that the results of 
				the survey are unaltered. Lastly, it's possible to assume that every label that identifies a group more general than a single specie, like a family or a whole order is referred to the most 
				common specie of that family or order. The only way to know exactly which of these possibilities performs better is conducting some experiments and compare the obtained results.

		\noindent Even with all these problems, the survey works quite well, since also with a few answers the results show that most of the subjects had mentioned the most common birds, like pigeons, while the 
		less common ones, like for examples peacocks, are mentioned fewer times. The results of this particular survey show that, a part for some examples, most of the birds appear only a few times. Although there 
		are some examples that are most likely outliers even with large numbers of subjects taking the survey, like ``Dodo'', some other examples, like ``Swift'' or ``Common blackbird'', 
		are likely to be more typical with a larger number of people taking the survey.\\
		The goal of the survey is to infer a measure of typicality based on how often a certain example appears in the results of the answers, and the result, at first glance, seems to be achieved. Although only 
		a test can prove this, it's very likely that with a larger group of subjects taking the survey, the results will differ more than with a small number of subjects.

	\newpage
